\textbf{NBA Party}

### 2017-05-05 init_model.rnw
Added a plot of running profits from betting in 2016.

m <- glm(outcome == 'W' ~ party + lag.chg.pos + travel.dist + 
             nhours.lgame + I(hour(date)),
         data = lines[season < 2017], family = 'binomial',
         na.action = 'na.exclude')

@@

lm(demeaned.reb.per.min ~ party + lag.chg.pos +
       I(log(travel.dist+1)/nhours.lgame) + nhours.lgame,
   data = data[season < 2017 & last.game.loc != team] %>% na.omit) %>%
   summary
@

@@

sum(b, na.rm = T)
@

>>>>

lines[, ew := sin(travel.dir %% 360 / 360 * 2 * pi)]
#plot(lines$travel.dir, lines$ew)

m <- glm(outcome == 'W' ~ party + lag.chg.pos + travel.dist*ew + 
             nhours.lgame + I(hour(date)),
         data = lines[season < 2017], family = 'binomial',
         na.action = 'na.exclude')

@@

lm(demeaned.reb.per.min ~ party + lag.chg.pos + travel.dist + nhours.lgame,
   data = data[last.game.loc != team] %>% na.omit) %>%
   summary
@

@@

sum(b, na.rm = T)

### 
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 2)
